---
title: "Fieldwork"
page-layout: full
code-tools: false
---

These are a selection of photos from places at which I have had the immense privilege to work.

## Santa Barbara Coastal Long-Term Ecological Research sites, California

::: column-page
```{r}
#| echo: false
library(pixture)

pixgallery(
  list.files("images/fieldwork/sbc", 
             full.names = TRUE),
  caption = c("Kelp off Isla Vista Reef, Summer 2021.",
             "Kelp off Mohawk Reef, Summer 2021.",
             "Kelp off Mohawk Reef, Summer 2021.",
             "White Shark off Carpinteria Reef, Summer 2021."),
  dim = "200px",
  gap = "10px"
)
```
:::

## Coto Brus canton, Costa Rica

::: column-page
```{r}
#| echo: false

pixgallery(
  list.files("images/fieldwork/coto-brus", 
             full.names = TRUE),
  caption = c("View of Loma Linda farm, Spring 2022.",
             "Measuring seedlings, Spring 2022.",
             "Freshly constructed seedling cage, Spring 2022.",
             "Seedlings in cage, Summer 2022."),
  dim = "200px",
  gap = "10px"
)
```
:::

## Tejon Ranch Conservancy, California

::: column-page
```{r}
#| echo: false

pixgallery(
  list.files("images/fieldwork/tejon", 
             full.names = TRUE),
  caption = c("Michelle during one of our breaks sampling vegetation, Spring 2017.",
             "Holly, Michelle, and Devyn sampling soil for Bui et al. 2020, Spring 2018.",
             "Deer amongst oak trees, Summer 2016.",
             "Bella, Devyn, Carina, and me, Summer 2016."),
  dim = "200px",
  gap = "10px"
)
```
:::

## Santa Barbara Island, California

::: column-page
```{r}
#| echo: false

pixgallery(
  list.files("images/fieldwork/sbi", 
             full.names = TRUE),
  caption = c("View out the researcher cabin.",
             "Cove.",
             "Resting sea lions.",
             "Western Gull chick."),
  dim = "200px",
  gap = "10px"
)
```
:::

## Palmyra Atoll, USA

::: column-page
```{r}
#| echo: false

pixgallery(
  list.files("images/fieldwork/palmyra", 
             full.names = TRUE),
  caption = c("Me with Berlese funnels I sewed.",
             "Coconut and hermit crabs eating a tagged coconut for Miller-ter Kuile 2020.",
             "Glassy lagoon.",
             "Manta Ray at the dock."),
  dim = "200px",
  gap = "10px"
)
```
:::

## Code note

I drew my inspiration from Chris Gebhard's jolly data blog, specifically the page of [different data visualizations](https://jollydata.blog/challenges.html) for which there is code [here](https://github.com/nucleic-acid/quarto-blog/blob/main/challenges.qmd). See the {pixture} [package page](https://www.royfrancis.com/pixture/) for details, and my code to create this page [here](https://github.com/an-bui/an-bui/blob/main/fieldwork.qmd) (directly taken from Chris's code).
